Comparison of Terrain Following and Cut Cell Grids using a Non-Hydrostatic Model

### 2015-10-28 src/tf-cutcell-comparison/tf-cutcell-comparison.tex
remove plots that aren't needed, add GW cut cell 50dz result

\bibpunct{(}{)}{;}{a}{}{,}
\newcommand{\TODO}[1]{\textcolor{purple}{TODO: \emph{#1}}}

@@

\begin{figure*}
	\centering
	\includegraphics{../fig-gravityWaves-sampleLine/fig-gravityWaves-sampleLine.pdf}
%
	\caption{Vertical profiles of potential temperature differences between the start and end of the gravity waves test on (a) the BTF grid, and (b) the cut cell grid.  Results are compared with thermal advection tests results, showing differences in tracer density between the numeric and analytic solutions at $t = \SI{18000}{\second}$ on (c) the BTF grid, and (d) the cut cell grid.  The results are convergent, with the exception of the cut cell grid at $\Delta z = \SI{500}{\meter}$, and errors are found in the lowest layers on the cut cell grids.  \TODO{add GW cut cell dz=50m once the test has completed}}
	\label{fig:gw-sampleLine}
\end{figure*}

>>>>

\bibpunct{(}{)}{;}{a}{}{,}

@@

\begin{figure*}
	\centering
	\includegraphics{../fig-gravityWaves-sampleLine/fig-gravityWaves-sampleLine.pdf}
%
	\caption{Vertical profiles of potential temperature differences between the start and end of the gravity waves test on (a) the BTF grid, and (b) the cut cell grid.  Results are compared with thermal advection tests results, showing differences in tracer density between the numeric and analytic solutions at $t = \SI{18000}{\second}$ on (c) the BTF grid, and (d) the cut cell grid.  The results are convergent, except for errors found in the lowest layers on the cut cell grids.}
	\label{fig:gw-sampleLine}
\end{figure*}
